---
title: "DensityReport"
output:
  html_document:
    df_print: paged
---

# Human

### NMD

```{r setupHumanNMDMouse, echo=FALSE, out.width="50%", warning=FALSE}
NMDDenseFirst=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-13.21.38_new_NMD/All_AA_density_first_ORF.tsv',
  sep = '\t', header = TRUE)

NMDDenseSecond=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-13.21.38_new_NMD/All_AA_density_second_ORF.tsv',
  sep = '\t', header = TRUE)


RIDenseFirst=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-15.10.13_new_RI/All_AA_density_first_ORF.tsv',
  sep = '\t', header = TRUE)

RIDenseSecond=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-15.10.13_new_RI/All_AA_density_second_ORF.tsv',
  sep = '\t', header = TRUE)


CodingDense=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Input/human/All_AA_density.tsv',
  sep = '\t', header = TRUE)

NMDdensitiesA = c("First ORF" = list(NMDDenseFirst[,2]),"Second ORF" = list(NMDDenseSecond[,2]),"Coding transcripts" = list(CodingDense[,2]))
NMDdensitiesR = c("First ORF" = list(NMDDenseFirst[,3]),"Second ORF" = list(NMDDenseSecond[,3]),"Coding transcripts" = list(CodingDense[,3]))
NMDdensitiesN = c("First ORF" = list(NMDDenseFirst[,4]),"Second ORF" = list(NMDDenseSecond[,4]),"Coding transcripts" = list(CodingDense[,4]))
NMDdensitiesD = c("First ORF" = list(NMDDenseFirst[,5]),"Second ORF" = list(NMDDenseSecond[,5]),"Coding transcripts" = list(CodingDense[,5]))
NMDdensitiesC = c("First ORF" = list(NMDDenseFirst[,6]),"Second ORF" = list(NMDDenseSecond[,6]),"Coding transcripts" = list(CodingDense[,6]))
NMDdensitiesQ = c("First ORF" = list(NMDDenseFirst[,7]),"Second ORF" = list(NMDDenseSecond[,7]),"Coding transcripts" = list(CodingDense[,7]))
NMDdensitiesG = c("First ORF" = list(NMDDenseFirst[,8]),"Second ORF" = list(NMDDenseSecond[,8]),"Coding transcripts" = list(CodingDense[,8]))
NMDdensitiesE = c("First ORF" = list(NMDDenseFirst[,9]),"Second ORF" = list(NMDDenseSecond[,9]),"Coding transcripts" = list(CodingDense[,9]))
NMDdensitiesH = c("First ORF" = list(NMDDenseFirst[,10]),"Second ORF" = list(NMDDenseSecond[,10]),"Coding transcripts" = list(CodingDense[,10]))
NMDdensitiesI = c("First ORF" = list(NMDDenseFirst[,11]),"Second ORF" = list(NMDDenseSecond[,11]),"Coding transcripts" = list(CodingDense[,11]))
NMDdensitiesL = c("First ORF" = list(NMDDenseFirst[,12]),"Second ORF" = list(NMDDenseSecond[,12]),"Coding transcripts" = list(CodingDense[,12]))
NMDdensitiesK = c("First ORF" = list(NMDDenseFirst[,13]),"Second ORF" = list(NMDDenseSecond[,13]),"Coding transcripts" = list(CodingDense[,13]))
NMDdensitiesM = c("First ORF" = list(NMDDenseFirst[,14]),"Second ORF" = list(NMDDenseSecond[,14]),"Coding transcripts" = list(CodingDense[,14]))
NMDdensitiesF = c("First ORF" = list(NMDDenseFirst[,15]),"Second ORF" = list(NMDDenseSecond[,15]),"Coding transcripts" = list(CodingDense[,15]))
NMDdensitiesP = c("First ORF" = list(NMDDenseFirst[,16]),"Second ORF" = list(NMDDenseSecond[,16]),"Coding transcripts" = list(CodingDense[,16]))
NMDdensitiesS = c("First ORF" = list(NMDDenseFirst[,17]),"Second ORF" = list(NMDDenseSecond[,17]),"Coding transcripts" = list(CodingDense[,17]))
NMDdensitiesT = c("First ORF" = list(NMDDenseFirst[,18]),"Second ORF" = list(NMDDenseSecond[,18]),"Coding transcripts" = list(CodingDense[,18]))
NMDdensitiesW = c("First ORF" = list(NMDDenseFirst[,19]),"Second ORF" = list(NMDDenseSecond[,19]),"Coding transcripts" = list(CodingDense[,19]))
NMDdensitiesY = c("First ORF" = list(NMDDenseFirst[,20]),"Second ORF" = list(NMDDenseSecond[,20]),"Coding transcripts" = list(CodingDense[,20]))
NMDdensitiesV = c("First ORF" = list(NMDDenseFirst[,21]),"Second ORF" = list(NMDDenseSecond[,21]),"Coding transcripts" = list(CodingDense[,21]))

#par(mfrow=c(10,2))


boxplot(NMDdensitiesA,ylab="Density",outline = FALSE, main = "Alanine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesR,ylab="Density",outline = FALSE, main = "Arginine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesN,ylab="Density",outline = FALSE, main = "Asparagine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesD,ylab="Density",outline = FALSE, main = "Aspartic acid density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesC,ylab="Density",outline = FALSE, main = "Cysteine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesQ,ylab="Density",outline = FALSE, main = "Glutamine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesG,ylab="Density",outline = FALSE, main = "Glycine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesE,ylab="Density",outline = FALSE, main = "Glutamic acid density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesH,ylab="Density",outline = FALSE, main = "Histidine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesI,ylab="Density",outline = FALSE, main = "Isoleucine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesL,ylab="Density",outline = FALSE, main = "Leucine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesK,ylab="Density",outline = FALSE, main = "Lysine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesM,ylab="Density",outline = FALSE, main = "Methionine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesF,ylab="Density",outline = FALSE, main = "Phenylalanine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesP,ylab="Density",outline = FALSE, main = "Proline density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesS,ylab="Density",outline = FALSE, main = "Serine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesT,ylab="Density",outline = FALSE, main = "Threonine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesW,ylab="Density",outline = FALSE, main = "Tryptophan density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesY,ylab="Density",outline = FALSE, main = "Tyrosine density for unique regions and protein coding transcripts")
boxplot(NMDdensitiesV,ylab="Density",outline = FALSE, main = "Valine density for unique regions and protein coding transcripts")
```

### T-test between unique Protein Regions in first ORF and unique Protein Regions in second ORF:

```{r, echo= FALSE}
cat("Alananine:")
t.test(NMDdensitiesA[[1]],NMDdensitiesA[[2]])
cat("Arginine")
t.test(NMDdensitiesR[[1]],NMDdensitiesR[[2]])
cat("Asparagine")
t.test(NMDdensitiesN[[1]],NMDdensitiesN[[2]])
cat("Aspartic acid")
t.test(NMDdensitiesD[[1]],NMDdensitiesD[[2]])
cat("Cysteine")
t.test(NMDdensitiesC[[1]],NMDdensitiesC[[2]])
cat("Glutamine")
t.test(NMDdensitiesQ[[1]],NMDdensitiesQ[[2]])
cat("Glycine")
t.test(NMDdensitiesG[[1]],NMDdensitiesG[[2]])
cat("Glutamic acid")
t.test(NMDdensitiesE[[1]],NMDdensitiesE[[2]])
cat("Histidine")
t.test(NMDdensitiesH[[1]],NMDdensitiesH[[2]])
cat("Isoleucine")
t.test(NMDdensitiesI[[1]],NMDdensitiesI[[2]])
cat("Leucine")
t.test(NMDdensitiesL[[1]],NMDdensitiesL[[2]])
cat("Lysine")
t.test(NMDdensitiesK[[1]],NMDdensitiesK[[2]])
cat("Methionine")
t.test(NMDdensitiesM[[1]],NMDdensitiesM[[2]])
cat("Phenylalanine")
t.test(NMDdensitiesF[[1]],NMDdensitiesF[[2]])
cat("Proline")
t.test(NMDdensitiesP[[1]],NMDdensitiesP[[2]])
cat("Serine")
t.test(NMDdensitiesS[[1]],NMDdensitiesS[[2]])
cat("Threonine")
t.test(NMDdensitiesT[[1]],NMDdensitiesT[[2]])
cat("Tryptophan")
t.test(NMDdensitiesW[[1]],NMDdensitiesW[[2]])
cat("Tyrosine")
t.test(NMDdensitiesY[[1]],NMDdensitiesY[[2]])
cat("Valine")
t.test(NMDdensitiesV[[1]],NMDdensitiesV[[2]])
```

### T-test between unique Protein Regions in first ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(NMDdensitiesA[[1]],NMDdensitiesA[[3]])
cat("Arginine")
t.test(NMDdensitiesR[[1]],NMDdensitiesR[[3]])
cat("Asparagine")
t.test(NMDdensitiesN[[1]],NMDdensitiesN[[3]])
cat("Aspartic acid")
t.test(NMDdensitiesD[[1]],NMDdensitiesD[[3]])
cat("Cysteine")
t.test(NMDdensitiesC[[1]],NMDdensitiesC[[3]])
cat("Glutamine")
t.test(NMDdensitiesQ[[1]],NMDdensitiesQ[[3]])
cat("Glycine")
t.test(NMDdensitiesG[[1]],NMDdensitiesG[[3]])
cat("Glutamic acid")
t.test(NMDdensitiesE[[1]],NMDdensitiesE[[3]])
cat("Histidine")
t.test(NMDdensitiesH[[1]],NMDdensitiesH[[3]])
cat("Isoleucine")
t.test(NMDdensitiesI[[1]],NMDdensitiesI[[3]])
cat("Leucine")
t.test(NMDdensitiesL[[1]],NMDdensitiesL[[3]])
cat("Lysine")
t.test(NMDdensitiesK[[1]],NMDdensitiesK[[3]])
cat("Methionine")
t.test(NMDdensitiesM[[1]],NMDdensitiesM[[3]])
cat("Phenylalanine")
t.test(NMDdensitiesF[[1]],NMDdensitiesF[[3]])
cat("Proline")
t.test(NMDdensitiesP[[1]],NMDdensitiesP[[3]])
cat("Serine")
t.test(NMDdensitiesS[[1]],NMDdensitiesS[[3]])
cat("Threonine")
t.test(NMDdensitiesT[[1]],NMDdensitiesT[[3]])
cat("Tryptophan")
t.test(NMDdensitiesW[[1]],NMDdensitiesW[[3]])
cat("Tyrosine")
t.test(NMDdensitiesY[[1]],NMDdensitiesY[[3]])
cat("Valine")
t.test(NMDdensitiesV[[1]],NMDdensitiesV[[3]])
```

### T-test between unique Protein Regions in second ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(NMDdensitiesA[[2]],NMDdensitiesA[[3]])
cat("Arginine")
t.test(NMDdensitiesR[[2]],NMDdensitiesR[[3]])
cat("Asparagine")
t.test(NMDdensitiesN[[2]],NMDdensitiesN[[3]])
cat("Aspartic acid")
t.test(NMDdensitiesD[[2]],NMDdensitiesD[[3]])
cat("Cysteine")
t.test(NMDdensitiesC[[2]],NMDdensitiesC[[3]])
cat("Glutamine")
t.test(NMDdensitiesQ[[2]],NMDdensitiesQ[[3]])
cat("Glycine")
t.test(NMDdensitiesG[[2]],NMDdensitiesG[[3]])
cat("Glutamic acid")
t.test(NMDdensitiesE[[2]],NMDdensitiesE[[3]])
cat("Histidine")
t.test(NMDdensitiesH[[2]],NMDdensitiesH[[3]])
cat("Isoleucine")
t.test(NMDdensitiesI[[2]],NMDdensitiesI[[3]])
cat("Leucine")
t.test(NMDdensitiesL[[2]],NMDdensitiesL[[3]])
cat("Lysine")
t.test(NMDdensitiesK[[2]],NMDdensitiesK[[3]])
cat("Methionine")
t.test(NMDdensitiesM[[2]],NMDdensitiesM[[3]])
cat("Phenylalanine")
t.test(NMDdensitiesF[[2]],NMDdensitiesF[[3]])
cat("Proline")
t.test(NMDdensitiesP[[2]],NMDdensitiesP[[3]])
cat("Serine")
t.test(NMDdensitiesS[[2]],NMDdensitiesS[[3]])
cat("Threonine")
t.test(NMDdensitiesT[[2]],NMDdensitiesT[[3]])
cat("Tryptophan")
t.test(NMDdensitiesW[[2]],NMDdensitiesW[[3]])
cat("Tyrosine")
t.test(NMDdensitiesY[[2]],NMDdensitiesY[[3]])
cat("Valine")
t.test(NMDdensitiesV[[2]],NMDdensitiesV[[3]])
```

### RI


```{r setupHumanRI, echo=FALSE, fig.show="hold", out.width="50%", warning=FALSE}
RIdensitiesA = c("First ORF" = list(RIDenseFirst[,2]),"Second ORF" = list(RIDenseSecond[,2]),"Coding transcripts" = list(CodingDense[,2]))
RIdensitiesR = c("First ORF" = list(RIDenseFirst[,3]),"Second ORF" = list(RIDenseSecond[,3]),"Coding transcripts" = list(CodingDense[,3]))
RIdensitiesN = c("First ORF" = list(RIDenseFirst[,4]),"Second ORF" = list(RIDenseSecond[,4]),"Coding transcripts" = list(CodingDense[,4]))
RIdensitiesD = c("First ORF" = list(RIDenseFirst[,5]),"Second ORF" = list(RIDenseSecond[,5]),"Coding transcripts" = list(CodingDense[,5]))
RIdensitiesC = c("First ORF" = list(RIDenseFirst[,6]),"Second ORF" = list(RIDenseSecond[,6]),"Coding transcripts" = list(CodingDense[,6]))
RIdensitiesQ = c("First ORF" = list(RIDenseFirst[,7]),"Second ORF" = list(RIDenseSecond[,7]),"Coding transcripts" = list(CodingDense[,7]))
RIdensitiesG = c("First ORF" = list(RIDenseFirst[,8]),"Second ORF" = list(RIDenseSecond[,8]),"Coding transcripts" = list(CodingDense[,8]))
RIdensitiesE = c("First ORF" = list(RIDenseFirst[,9]),"Second ORF" = list(RIDenseSecond[,9]),"Coding transcripts" = list(CodingDense[,9]))
RIdensitiesH = c("First ORF" = list(RIDenseFirst[,10]),"Second ORF" = list(RIDenseSecond[,10]),"Coding transcripts" = list(CodingDense[,10]))
RIdensitiesI = c("First ORF" = list(RIDenseFirst[,11]),"Second ORF" = list(RIDenseSecond[,11]),"Coding transcripts" = list(CodingDense[,11]))
RIdensitiesL = c("First ORF" = list(RIDenseFirst[,12]),"Second ORF" = list(RIDenseSecond[,12]),"Coding transcripts" = list(CodingDense[,12]))
RIdensitiesK = c("First ORF" = list(RIDenseFirst[,13]),"Second ORF" = list(RIDenseSecond[,13]),"Coding transcripts" = list(CodingDense[,13]))
RIdensitiesM = c("First ORF" = list(RIDenseFirst[,14]),"Second ORF" = list(RIDenseSecond[,14]),"Coding transcripts" = list(CodingDense[,14]))
RIdensitiesF = c("First ORF" = list(RIDenseFirst[,15]),"Second ORF" = list(RIDenseSecond[,15]),"Coding transcripts" = list(CodingDense[,15]))
RIdensitiesP = c("First ORF" = list(RIDenseFirst[,16]),"Second ORF" = list(RIDenseSecond[,16]),"Coding transcripts" = list(CodingDense[,16]))
RIdensitiesS = c("First ORF" = list(RIDenseFirst[,17]),"Second ORF" = list(RIDenseSecond[,17]),"Coding transcripts" = list(CodingDense[,17]))
RIdensitiesT = c("First ORF" = list(RIDenseFirst[,18]),"Second ORF" = list(RIDenseSecond[,18]),"Coding transcripts" = list(CodingDense[,18]))
RIdensitiesW = c("First ORF" = list(RIDenseFirst[,19]),"Second ORF" = list(RIDenseSecond[,19]),"Coding transcripts" = list(CodingDense[,19]))
RIdensitiesY = c("First ORF" = list(RIDenseFirst[,20]),"Second ORF" = list(RIDenseSecond[,20]),"Coding transcripts" = list(CodingDense[,20]))
RIdensitiesV = c("First ORF" = list(RIDenseFirst[,21]),"Second ORF" = list(RIDenseSecond[,21]),"Coding transcripts" = list(CodingDense[,21]))

#par(mfrow=c(10,2))


boxplot(RIdensitiesA,ylab="Density",outline = FALSE, main = "Alanine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesR,ylab="Density",outline = FALSE, main = "Arginine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesN,ylab="Density",outline = FALSE, main = "Asparagine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesD,ylab="Density",outline = FALSE, main = "Aspartic acid density for unique regions and protein coding transcripts")
boxplot(RIdensitiesC,ylab="Density",outline = FALSE, main = "Cysteine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesQ,ylab="Density",outline = FALSE, main = "Glutamine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesG,ylab="Density",outline = FALSE, main = "Glycine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesE,ylab="Density",outline = FALSE, main = "Glutamic acid density for unique regions and protein coding transcripts")
boxplot(RIdensitiesH,ylab="Density",outline = FALSE, main = "Histidine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesI,ylab="Density",outline = FALSE, main = "Isoleucine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesL,ylab="Density",outline = FALSE, main = "Leucine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesK,ylab="Density",outline = FALSE, main = "Lysine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesM,ylab="Density",outline = FALSE, main = "Methionine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesF,ylab="Density",outline = FALSE, main = "Phenylalanine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesP,ylab="Density",outline = FALSE, main = "Proline density for unique regions and protein coding transcripts")
boxplot(RIdensitiesS,ylab="Density",outline = FALSE, main = "Serine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesT,ylab="Density",outline = FALSE, main = "Threonine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesW,ylab="Density",outline = FALSE, main = "Tryptophan density for unique regions and protein coding transcripts")
boxplot(RIdensitiesY,ylab="Density",outline = FALSE, main = "Tyrosine density for unique regions and protein coding transcripts")
boxplot(RIdensitiesV,ylab="Density",outline = FALSE, main = "Valine density for unique regions and protein coding transcripts")
```

### T-test between unique Protein Regions in first ORF and unique Protein Regions in second ORF:

```{r, echo= FALSE}
cat("Alananine:")
t.test(RIdensitiesA[[1]],RIdensitiesA[[2]])
cat("Arginine")
t.test(RIdensitiesR[[1]],RIdensitiesR[[2]])
cat("Asparagine")
t.test(RIdensitiesN[[1]],RIdensitiesN[[2]])
cat("Aspartic acid")
t.test(RIdensitiesD[[1]],RIdensitiesD[[2]])
cat("Cysteine")
t.test(RIdensitiesC[[1]],RIdensitiesC[[2]])
cat("Glutamine")
t.test(RIdensitiesQ[[1]],RIdensitiesQ[[2]])
cat("Glycine")
t.test(RIdensitiesG[[1]],RIdensitiesG[[2]])
cat("Glutamic acid")
t.test(RIdensitiesE[[1]],RIdensitiesE[[2]])
cat("Histidine")
t.test(RIdensitiesH[[1]],RIdensitiesH[[2]])
cat("Isoleucine")
t.test(RIdensitiesI[[1]],RIdensitiesI[[2]])
cat("Leucine")
t.test(RIdensitiesL[[1]],RIdensitiesL[[2]])
cat("Lysine")
t.test(RIdensitiesK[[1]],RIdensitiesK[[2]])
cat("Methionine")
t.test(RIdensitiesM[[1]],RIdensitiesM[[2]])
cat("Phenylalanine")
t.test(RIdensitiesF[[1]],RIdensitiesF[[2]])
cat("Proline")
t.test(RIdensitiesP[[1]],RIdensitiesP[[2]])
cat("Serine")
t.test(RIdensitiesS[[1]],RIdensitiesS[[2]])
cat("Threonine")
t.test(RIdensitiesT[[1]],RIdensitiesT[[2]])
cat("Tryptophan")
t.test(RIdensitiesW[[1]],RIdensitiesW[[2]])
cat("Tyrosine")
t.test(RIdensitiesY[[1]],RIdensitiesY[[2]])
cat("Valine")
t.test(RIdensitiesV[[1]],RIdensitiesV[[2]])
```


### T-test between unique Protein Regions in first ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(RIdensitiesA[[1]],RIdensitiesA[[3]])
cat("Arginine")
t.test(RIdensitiesR[[1]],RIdensitiesR[[3]])
cat("Asparagine")
t.test(RIdensitiesN[[1]],RIdensitiesN[[3]])
cat("Aspartic acid")
t.test(RIdensitiesD[[1]],RIdensitiesD[[3]])
cat("Cysteine")
t.test(RIdensitiesC[[1]],RIdensitiesC[[3]])
cat("Glutamine")
t.test(RIdensitiesQ[[1]],RIdensitiesQ[[3]])
cat("Glycine")
t.test(RIdensitiesG[[1]],RIdensitiesG[[3]])
cat("Glutamic acid")
t.test(RIdensitiesE[[1]],RIdensitiesE[[3]])
cat("Histidine")
t.test(RIdensitiesH[[1]],RIdensitiesH[[3]])
cat("Isoleucine")
t.test(RIdensitiesI[[1]],RIdensitiesI[[3]])
cat("Leucine")
t.test(RIdensitiesL[[1]],RIdensitiesL[[3]])
cat("Lysine")
t.test(RIdensitiesK[[1]],RIdensitiesK[[3]])
cat("Methionine")
t.test(RIdensitiesM[[1]],RIdensitiesM[[3]])
cat("Phenylalanine")
t.test(RIdensitiesF[[1]],RIdensitiesF[[3]])
cat("Proline")
t.test(RIdensitiesP[[1]],RIdensitiesP[[3]])
cat("Serine")
t.test(RIdensitiesS[[1]],RIdensitiesS[[3]])
cat("Threonine")
t.test(RIdensitiesT[[1]],RIdensitiesT[[3]])
cat("Tryptophan")
t.test(RIdensitiesW[[1]],RIdensitiesW[[3]])
cat("Tyrosine")
t.test(RIdensitiesY[[1]],RIdensitiesY[[3]])
cat("Valine")
t.test(RIdensitiesV[[1]],RIdensitiesV[[3]])
```


### T-test between unique Protein Regions in second ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(RIdensitiesA[[2]],RIdensitiesA[[3]])
cat("Arginine")
t.test(RIdensitiesR[[2]],RIdensitiesR[[3]])
cat("Asparagine")
t.test(RIdensitiesN[[2]],RIdensitiesN[[3]])
cat("Aspartic acid")
t.test(RIdensitiesD[[2]],RIdensitiesD[[3]])
cat("Cysteine")
t.test(RIdensitiesC[[2]],RIdensitiesC[[3]])
cat("Glutamine")
t.test(RIdensitiesQ[[2]],RIdensitiesQ[[3]])
cat("Glycine")
t.test(RIdensitiesG[[2]],RIdensitiesG[[3]])
cat("Glutamic acid")
t.test(RIdensitiesE[[2]],RIdensitiesE[[3]])
cat("Histidine")
t.test(RIdensitiesH[[2]],RIdensitiesH[[3]])
cat("Isoleucine")
t.test(RIdensitiesI[[2]],RIdensitiesI[[3]])
cat("Leucine")
t.test(RIdensitiesL[[2]],RIdensitiesL[[3]])
cat("Lysine")
t.test(RIdensitiesK[[2]],RIdensitiesK[[3]])
cat("Methionine")
t.test(RIdensitiesM[[2]],RIdensitiesM[[3]])
cat("Phenylalanine")
t.test(RIdensitiesF[[2]],RIdensitiesF[[3]])
cat("Proline")
t.test(RIdensitiesP[[2]],RIdensitiesP[[3]])
cat("Serine")
t.test(RIdensitiesS[[2]],RIdensitiesS[[3]])
cat("Threonine")
t.test(RIdensitiesT[[2]],RIdensitiesT[[3]])
cat("Tryptophan")
t.test(RIdensitiesW[[2]],RIdensitiesW[[3]])
cat("Tyrosine")
t.test(RIdensitiesY[[2]],RIdensitiesY[[3]])
cat("Valine")
t.test(RIdensitiesV[[2]],RIdensitiesV[[3]])
```



# Mouse

### NMD

```{r setupMouseNMD, echo=FALSE, out.width="50%", warning=FALSE}
NMDMouseDenseFirst=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_15.07.2021-12.20.56_NMD_mouse/All_AA_density_first_ORF.tsv',
  sep = '\t', header = TRUE)

NMDMouseDenseSecond=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_15.07.2021-12.20.56_NMD_mouse/All_AA_density_second_ORF.tsv',
  sep = '\t', header = TRUE)


RIMouseDenseFirst=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_15.07.2021-13.02.13_RI_mouse/All_AA_density_first_ORF.tsv',
  sep = '\t', header = TRUE)

RIMouseDenseSecond=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_15.07.2021-13.02.13_RI_mouse/All_AA_density_second_ORF.tsv',
  sep = '\t', header = TRUE)


CodingMouseDense=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/Raw-Data/Mouse/All_AA_density.tsv',
  sep = '\t', header = TRUE)

NMDMousedensitiesA = c("First ORF" = list(NMDMouseDenseFirst[,2]),"Second ORF" = list(NMDMouseDenseSecond[,2]),"Coding transcripts" = list(CodingMouseDense[,2]))
NMDMousedensitiesR = c("First ORF" = list(NMDMouseDenseFirst[,3]),"Second ORF" = list(NMDMouseDenseSecond[,3]),"Coding transcripts" = list(CodingMouseDense[,3]))
NMDMousedensitiesN = c("First ORF" = list(NMDMouseDenseFirst[,4]),"Second ORF" = list(NMDMouseDenseSecond[,4]),"Coding transcripts" = list(CodingMouseDense[,4]))
NMDMousedensitiesD = c("First ORF" = list(NMDMouseDenseFirst[,5]),"Second ORF" = list(NMDMouseDenseSecond[,5]),"Coding transcripts" = list(CodingMouseDense[,5]))
NMDMousedensitiesC = c("First ORF" = list(NMDMouseDenseFirst[,6]),"Second ORF" = list(NMDMouseDenseSecond[,6]),"Coding transcripts" = list(CodingMouseDense[,6]))
NMDMousedensitiesQ = c("First ORF" = list(NMDMouseDenseFirst[,7]),"Second ORF" = list(NMDMouseDenseSecond[,7]),"Coding transcripts" = list(CodingMouseDense[,7]))
NMDMousedensitiesG = c("First ORF" = list(NMDMouseDenseFirst[,8]),"Second ORF" = list(NMDMouseDenseSecond[,8]),"Coding transcripts" = list(CodingMouseDense[,8]))
NMDMousedensitiesE = c("First ORF" = list(NMDMouseDenseFirst[,9]),"Second ORF" = list(NMDMouseDenseSecond[,9]),"Coding transcripts" = list(CodingMouseDense[,9]))
NMDMousedensitiesH = c("First ORF" = list(NMDMouseDenseFirst[,10]),"Second ORF" = list(NMDMouseDenseSecond[,10]),"Coding transcripts" = list(CodingMouseDense[,10]))
NMDMousedensitiesI = c("First ORF" = list(NMDMouseDenseFirst[,11]),"Second ORF" = list(NMDMouseDenseSecond[,11]),"Coding transcripts" = list(CodingMouseDense[,11]))
NMDMousedensitiesL = c("First ORF" = list(NMDMouseDenseFirst[,12]),"Second ORF" = list(NMDMouseDenseSecond[,12]),"Coding transcripts" = list(CodingMouseDense[,12]))
NMDMousedensitiesK = c("First ORF" = list(NMDMouseDenseFirst[,13]),"Second ORF" = list(NMDMouseDenseSecond[,13]),"Coding transcripts" = list(CodingMouseDense[,13]))
NMDMousedensitiesM = c("First ORF" = list(NMDMouseDenseFirst[,14]),"Second ORF" = list(NMDMouseDenseSecond[,14]),"Coding transcripts" = list(CodingMouseDense[,14]))
NMDMousedensitiesF = c("First ORF" = list(NMDMouseDenseFirst[,15]),"Second ORF" = list(NMDMouseDenseSecond[,15]),"Coding transcripts" = list(CodingMouseDense[,15]))
NMDMousedensitiesP = c("First ORF" = list(NMDMouseDenseFirst[,16]),"Second ORF" = list(NMDMouseDenseSecond[,16]),"Coding transcripts" = list(CodingMouseDense[,16]))
NMDMousedensitiesS = c("First ORF" = list(NMDMouseDenseFirst[,17]),"Second ORF" = list(NMDMouseDenseSecond[,17]),"Coding transcripts" = list(CodingMouseDense[,17]))
NMDMousedensitiesT = c("First ORF" = list(NMDMouseDenseFirst[,18]),"Second ORF" = list(NMDMouseDenseSecond[,18]),"Coding transcripts" = list(CodingMouseDense[,18]))
NMDMousedensitiesW = c("First ORF" = list(NMDMouseDenseFirst[,19]),"Second ORF" = list(NMDMouseDenseSecond[,19]),"Coding transcripts" = list(CodingMouseDense[,19]))
NMDMousedensitiesY = c("First ORF" = list(NMDMouseDenseFirst[,20]),"Second ORF" = list(NMDMouseDenseSecond[,20]),"Coding transcripts" = list(CodingMouseDense[,20]))
NMDMousedensitiesV = c("First ORF" = list(NMDMouseDenseFirst[,21]),"Second ORF" = list(NMDMouseDenseSecond[,21]),"Coding transcripts" = list(CodingMouseDense[,21]))

#par(mfrow=c(10,2))


boxplot(NMDMousedensitiesA,ylab="Density",outline = FALSE, main = "Alanine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesR,ylab="Density",outline = FALSE, main = "Arginine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesN,ylab="Density",outline = FALSE, main = "Asparagine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesD,ylab="Density",outline = FALSE, main = "Aspartic acid density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesC,ylab="Density",outline = FALSE, main = "Cysteine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesQ,ylab="Density",outline = FALSE, main = "Glutamine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesG,ylab="Density",outline = FALSE, main = "Glycine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesE,ylab="Density",outline = FALSE, main = "Glutamic acid density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesH,ylab="Density",outline = FALSE, main = "Histidine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesI,ylab="Density",outline = FALSE, main = "Isoleucine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesL,ylab="Density",outline = FALSE, main = "Leucine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesK,ylab="Density",outline = FALSE, main = "Lysine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesM,ylab="Density",outline = FALSE, main = "Methionine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesF,ylab="Density",outline = FALSE, main = "Phenylalanine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesP,ylab="Density",outline = FALSE, main = "Proline density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesS,ylab="Density",outline = FALSE, main = "Serine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesT,ylab="Density",outline = FALSE, main = "Threonine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesW,ylab="Density",outline = FALSE, main = "Tryptophan density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesY,ylab="Density",outline = FALSE, main = "Tyrosine density for unique regions and protein coding transcripts")
boxplot(NMDMousedensitiesV,ylab="Density",outline = FALSE, main = "Valine density for unique regions and protein coding transcripts")
```

### T-test between unique Protein Regions in first ORF and unique Protein Regions in second ORF:

```{r, echo= FALSE}
cat("Alananine:")
t.test(NMDMousedensitiesA[[1]],NMDMousedensitiesA[[2]])
cat("Arginine")
t.test(NMDMousedensitiesR[[1]],NMDMousedensitiesR[[2]])
cat("Asparagine")
t.test(NMDMousedensitiesN[[1]],NMDMousedensitiesN[[2]])
cat("Aspartic acid")
t.test(NMDMousedensitiesD[[1]],NMDMousedensitiesD[[2]])
cat("Cysteine")
t.test(NMDMousedensitiesC[[1]],NMDMousedensitiesC[[2]])
cat("Glutamine")
t.test(NMDMousedensitiesQ[[1]],NMDMousedensitiesQ[[2]])
cat("Glycine")
t.test(NMDMousedensitiesG[[1]],NMDMousedensitiesG[[2]])
cat("Glutamic acid")
t.test(NMDMousedensitiesE[[1]],NMDMousedensitiesE[[2]])
cat("Histidine")
t.test(NMDMousedensitiesH[[1]],NMDMousedensitiesH[[2]])
cat("Isoleucine")
t.test(NMDMousedensitiesI[[1]],NMDMousedensitiesI[[2]])
cat("Leucine")
t.test(NMDMousedensitiesL[[1]],NMDMousedensitiesL[[2]])
cat("Lysine")
t.test(NMDMousedensitiesK[[1]],NMDMousedensitiesK[[2]])
cat("Methionine")
t.test(NMDMousedensitiesM[[1]],NMDMousedensitiesM[[2]])
cat("Phenylalanine")
t.test(NMDMousedensitiesF[[1]],NMDMousedensitiesF[[2]])
cat("Proline")
t.test(NMDMousedensitiesP[[1]],NMDMousedensitiesP[[2]])
cat("Serine")
t.test(NMDMousedensitiesS[[1]],NMDMousedensitiesS[[2]])
cat("Threonine")
t.test(NMDMousedensitiesT[[1]],NMDMousedensitiesT[[2]])
cat("Tryptophan")
t.test(NMDMousedensitiesW[[1]],NMDMousedensitiesW[[2]])
cat("Tyrosine")
t.test(NMDMousedensitiesY[[1]],NMDMousedensitiesY[[2]])
cat("Valine")
t.test(NMDMousedensitiesV[[1]],NMDMousedensitiesV[[2]])
```

### T-test between unique Protein Regions in first ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(NMDMousedensitiesA[[1]],NMDMousedensitiesA[[3]])
cat("Arginine")
t.test(NMDMousedensitiesR[[1]],NMDMousedensitiesR[[3]])
cat("Asparagine")
t.test(NMDMousedensitiesN[[1]],NMDMousedensitiesN[[3]])
cat("Aspartic acid")
t.test(NMDMousedensitiesD[[1]],NMDMousedensitiesD[[3]])
cat("Cysteine")
t.test(NMDMousedensitiesC[[1]],NMDMousedensitiesC[[3]])
cat("Glutamine")
t.test(NMDMousedensitiesQ[[1]],NMDMousedensitiesQ[[3]])
cat("Glycine")
t.test(NMDMousedensitiesG[[1]],NMDMousedensitiesG[[3]])
cat("Glutamic acid")
t.test(NMDMousedensitiesE[[1]],NMDMousedensitiesE[[3]])
cat("Histidine")
t.test(NMDMousedensitiesH[[1]],NMDMousedensitiesH[[3]])
cat("Isoleucine")
t.test(NMDMousedensitiesI[[1]],NMDMousedensitiesI[[3]])
cat("Leucine")
t.test(NMDMousedensitiesL[[1]],NMDMousedensitiesL[[3]])
cat("Lysine")
t.test(NMDMousedensitiesK[[1]],NMDMousedensitiesK[[3]])
cat("Methionine")
t.test(NMDMousedensitiesM[[1]],NMDMousedensitiesM[[3]])
cat("Phenylalanine")
t.test(NMDMousedensitiesF[[1]],NMDMousedensitiesF[[3]])
cat("Proline")
t.test(NMDMousedensitiesP[[1]],NMDMousedensitiesP[[3]])
cat("Serine")
t.test(NMDMousedensitiesS[[1]],NMDMousedensitiesS[[3]])
cat("Threonine")
t.test(NMDMousedensitiesT[[1]],NMDMousedensitiesT[[3]])
cat("Tryptophan")
t.test(NMDMousedensitiesW[[1]],NMDMousedensitiesW[[3]])
cat("Tyrosine")
t.test(NMDMousedensitiesY[[1]],NMDMousedensitiesY[[3]])
cat("Valine")
t.test(NMDMousedensitiesV[[1]],NMDMousedensitiesV[[3]])
```

### T-test between unique Protein Regions in second ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(NMDMousedensitiesA[[2]],NMDMousedensitiesA[[3]])
cat("Arginine")
t.test(NMDMousedensitiesR[[2]],NMDMousedensitiesR[[3]])
cat("Asparagine")
t.test(NMDMousedensitiesN[[2]],NMDMousedensitiesN[[3]])
cat("Aspartic acid")
t.test(NMDMousedensitiesD[[2]],NMDMousedensitiesD[[3]])
cat("Cysteine")
t.test(NMDMousedensitiesC[[2]],NMDMousedensitiesC[[3]])
cat("Glutamine")
t.test(NMDMousedensitiesQ[[2]],NMDMousedensitiesQ[[3]])
cat("Glycine")
t.test(NMDMousedensitiesG[[2]],NMDMousedensitiesG[[3]])
cat("Glutamic acid")
t.test(NMDMousedensitiesE[[2]],NMDMousedensitiesE[[3]])
cat("Histidine")
t.test(NMDMousedensitiesH[[2]],NMDMousedensitiesH[[3]])
cat("Isoleucine")
t.test(NMDMousedensitiesI[[2]],NMDMousedensitiesI[[3]])
cat("Leucine")
t.test(NMDMousedensitiesL[[2]],NMDMousedensitiesL[[3]])
cat("Lysine")
t.test(NMDMousedensitiesK[[2]],NMDMousedensitiesK[[3]])
cat("Methionine")
t.test(NMDMousedensitiesM[[2]],NMDMousedensitiesM[[3]])
cat("Phenylalanine")
t.test(NMDMousedensitiesF[[2]],NMDMousedensitiesF[[3]])
cat("Proline")
t.test(NMDMousedensitiesP[[2]],NMDMousedensitiesP[[3]])
cat("Serine")
t.test(NMDMousedensitiesS[[2]],NMDMousedensitiesS[[3]])
cat("Threonine")
t.test(NMDMousedensitiesT[[2]],NMDMousedensitiesT[[3]])
cat("Tryptophan")
t.test(NMDMousedensitiesW[[2]],NMDMousedensitiesW[[3]])
cat("Tyrosine")
t.test(NMDMousedensitiesY[[2]],NMDMousedensitiesY[[3]])
cat("Valine")
t.test(NMDMousedensitiesV[[2]],NMDMousedensitiesV[[3]])
```

### RI


```{r setupMouseRI, echo=FALSE, fig.show="hold", out.width="50%", warning=FALSE}
RIMousedensitiesA = c("First ORF" = list(RIMouseDenseFirst[,2]),"Second ORF" = list(RIMouseDenseSecond[,2]),"Coding transcripts" = list(CodingMouseDense[,2]))
RIMousedensitiesR = c("First ORF" = list(RIMouseDenseFirst[,3]),"Second ORF" = list(RIMouseDenseSecond[,3]),"Coding transcripts" = list(CodingMouseDense[,3]))
RIMousedensitiesN = c("First ORF" = list(RIMouseDenseFirst[,4]),"Second ORF" = list(RIMouseDenseSecond[,4]),"Coding transcripts" = list(CodingMouseDense[,4]))
RIMousedensitiesD = c("First ORF" = list(RIMouseDenseFirst[,5]),"Second ORF" = list(RIMouseDenseSecond[,5]),"Coding transcripts" = list(CodingMouseDense[,5]))
RIMousedensitiesC = c("First ORF" = list(RIMouseDenseFirst[,6]),"Second ORF" = list(RIMouseDenseSecond[,6]),"Coding transcripts" = list(CodingMouseDense[,6]))
RIMousedensitiesQ = c("First ORF" = list(RIMouseDenseFirst[,7]),"Second ORF" = list(RIMouseDenseSecond[,7]),"Coding transcripts" = list(CodingMouseDense[,7]))
RIMousedensitiesG = c("First ORF" = list(RIMouseDenseFirst[,8]),"Second ORF" = list(RIMouseDenseSecond[,8]),"Coding transcripts" = list(CodingMouseDense[,8]))
RIMousedensitiesE = c("First ORF" = list(RIMouseDenseFirst[,9]),"Second ORF" = list(RIMouseDenseSecond[,9]),"Coding transcripts" = list(CodingMouseDense[,9]))
RIMousedensitiesH = c("First ORF" = list(RIMouseDenseFirst[,10]),"Second ORF" = list(RIMouseDenseSecond[,10]),"Coding transcripts" = list(CodingMouseDense[,10]))
RIMousedensitiesI = c("First ORF" = list(RIMouseDenseFirst[,11]),"Second ORF" = list(RIMouseDenseSecond[,11]),"Coding transcripts" = list(CodingMouseDense[,11]))
RIMousedensitiesL = c("First ORF" = list(RIMouseDenseFirst[,12]),"Second ORF" = list(RIMouseDenseSecond[,12]),"Coding transcripts" = list(CodingMouseDense[,12]))
RIMousedensitiesK = c("First ORF" = list(RIMouseDenseFirst[,13]),"Second ORF" = list(RIMouseDenseSecond[,13]),"Coding transcripts" = list(CodingMouseDense[,13]))
RIMousedensitiesM = c("First ORF" = list(RIMouseDenseFirst[,14]),"Second ORF" = list(RIMouseDenseSecond[,14]),"Coding transcripts" = list(CodingMouseDense[,14]))
RIMousedensitiesF = c("First ORF" = list(RIMouseDenseFirst[,15]),"Second ORF" = list(RIMouseDenseSecond[,15]),"Coding transcripts" = list(CodingMouseDense[,15]))
RIMousedensitiesP = c("First ORF" = list(RIMouseDenseFirst[,16]),"Second ORF" = list(RIMouseDenseSecond[,16]),"Coding transcripts" = list(CodingMouseDense[,16]))
RIMousedensitiesS = c("First ORF" = list(RIMouseDenseFirst[,17]),"Second ORF" = list(RIMouseDenseSecond[,17]),"Coding transcripts" = list(CodingMouseDense[,17]))
RIMousedensitiesT = c("First ORF" = list(RIMouseDenseFirst[,18]),"Second ORF" = list(RIMouseDenseSecond[,18]),"Coding transcripts" = list(CodingMouseDense[,18]))
RIMousedensitiesW = c("First ORF" = list(RIMouseDenseFirst[,19]),"Second ORF" = list(RIMouseDenseSecond[,19]),"Coding transcripts" = list(CodingMouseDense[,19]))
RIMousedensitiesY = c("First ORF" = list(RIMouseDenseFirst[,20]),"Second ORF" = list(RIMouseDenseSecond[,20]),"Coding transcripts" = list(CodingMouseDense[,20]))
RIMousedensitiesV = c("First ORF" = list(RIMouseDenseFirst[,21]),"Second ORF" = list(RIMouseDenseSecond[,21]),"Coding transcripts" = list(CodingMouseDense[,21]))

#par(mfrow=c(10,2))


boxplot(RIMousedensitiesA,ylab="Density",outline = FALSE, main = "Alanine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesR,ylab="Density",outline = FALSE, main = "Arginine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesN,ylab="Density",outline = FALSE, main = "Asparagine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesD,ylab="Density",outline = FALSE, main = "Aspartic acid density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesC,ylab="Density",outline = FALSE, main = "Cysteine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesQ,ylab="Density",outline = FALSE, main = "Glutamine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesG,ylab="Density",outline = FALSE, main = "Glycine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesE,ylab="Density",outline = FALSE, main = "Glutamic acid density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesH,ylab="Density",outline = FALSE, main = "Histidine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesI,ylab="Density",outline = FALSE, main = "Isoleucine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesL,ylab="Density",outline = FALSE, main = "Leucine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesK,ylab="Density",outline = FALSE, main = "Lysine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesM,ylab="Density",outline = FALSE, main = "Methionine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesF,ylab="Density",outline = FALSE, main = "Phenylalanine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesP,ylab="Density",outline = FALSE, main = "Proline density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesS,ylab="Density",outline = FALSE, main = "Serine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesT,ylab="Density",outline = FALSE, main = "Threonine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesW,ylab="Density",outline = FALSE, main = "Tryptophan density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesY,ylab="Density",outline = FALSE, main = "Tyrosine density for unique regions and protein coding transcripts")
boxplot(RIMousedensitiesV,ylab="Density",outline = FALSE, main = "Valine density for unique regions and protein coding transcripts")
```

### T-test between unique Protein Regions in first ORF and unique Protein Regions in second ORF:

```{r, echo= FALSE}
cat("Alananine:")
t.test(RIMousedensitiesA[[1]],RIMousedensitiesA[[2]])
cat("Arginine")
t.test(RIMousedensitiesR[[1]],RIMousedensitiesR[[2]])
cat("Asparagine")
t.test(RIMousedensitiesN[[1]],RIMousedensitiesN[[2]])
cat("Aspartic acid")
t.test(RIMousedensitiesD[[1]],RIMousedensitiesD[[2]])
cat("Cysteine")
t.test(RIMousedensitiesC[[1]],RIMousedensitiesC[[2]])
cat("Glutamine")
t.test(RIMousedensitiesQ[[1]],RIMousedensitiesQ[[2]])
cat("Glycine")
t.test(RIMousedensitiesG[[1]],RIMousedensitiesG[[2]])
cat("Glutamic acid")
t.test(RIMousedensitiesE[[1]],RIMousedensitiesE[[2]])
cat("Histidine")
t.test(RIMousedensitiesH[[1]],RIMousedensitiesH[[2]])
cat("Isoleucine")
t.test(RIMousedensitiesI[[1]],RIMousedensitiesI[[2]])
cat("Leucine")
t.test(RIMousedensitiesL[[1]],RIMousedensitiesL[[2]])
cat("Lysine")
t.test(RIMousedensitiesK[[1]],RIMousedensitiesK[[2]])
cat("Methionine")
t.test(RIMousedensitiesM[[1]],RIMousedensitiesM[[2]])
cat("Phenylalanine")
t.test(RIMousedensitiesF[[1]],RIMousedensitiesF[[2]])
cat("Proline")
t.test(RIMousedensitiesP[[1]],RIMousedensitiesP[[2]])
cat("Serine")
t.test(RIMousedensitiesS[[1]],RIMousedensitiesS[[2]])
cat("Threonine")
t.test(RIMousedensitiesT[[1]],RIMousedensitiesT[[2]])
cat("Tryptophan")
t.test(RIMousedensitiesW[[1]],RIMousedensitiesW[[2]])
cat("Tyrosine")
t.test(RIMousedensitiesY[[1]],RIMousedensitiesY[[2]])
cat("Valine")
t.test(RIMousedensitiesV[[1]],RIMousedensitiesV[[2]])
```


### T-test between unique Protein Regions in first ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(RIMousedensitiesA[[1]],RIMousedensitiesA[[3]])
cat("Arginine")
t.test(RIMousedensitiesR[[1]],RIMousedensitiesR[[3]])
cat("Asparagine")
t.test(RIMousedensitiesN[[1]],RIMousedensitiesN[[3]])
cat("Aspartic acid")
t.test(RIMousedensitiesD[[1]],RIMousedensitiesD[[3]])
cat("Cysteine")
t.test(RIMousedensitiesC[[1]],RIMousedensitiesC[[3]])
cat("Glutamine")
t.test(RIMousedensitiesQ[[1]],RIMousedensitiesQ[[3]])
cat("Glycine")
t.test(RIMousedensitiesG[[1]],RIMousedensitiesG[[3]])
cat("Glutamic acid")
t.test(RIMousedensitiesE[[1]],RIMousedensitiesE[[3]])
cat("Histidine")
t.test(RIMousedensitiesH[[1]],RIMousedensitiesH[[3]])
cat("Isoleucine")
t.test(RIMousedensitiesI[[1]],RIMousedensitiesI[[3]])
cat("Leucine")
t.test(RIMousedensitiesL[[1]],RIMousedensitiesL[[3]])
cat("Lysine")
t.test(RIMousedensitiesK[[1]],RIMousedensitiesK[[3]])
cat("Methionine")
t.test(RIMousedensitiesM[[1]],RIMousedensitiesM[[3]])
cat("Phenylalanine")
t.test(RIMousedensitiesF[[1]],RIMousedensitiesF[[3]])
cat("Proline")
t.test(RIMousedensitiesP[[1]],RIMousedensitiesP[[3]])
cat("Serine")
t.test(RIMousedensitiesS[[1]],RIMousedensitiesS[[3]])
cat("Threonine")
t.test(RIMousedensitiesT[[1]],RIMousedensitiesT[[3]])
cat("Tryptophan")
t.test(RIMousedensitiesW[[1]],RIMousedensitiesW[[3]])
cat("Tyrosine")
t.test(RIMousedensitiesY[[1]],RIMousedensitiesY[[3]])
cat("Valine")
t.test(RIMousedensitiesV[[1]],RIMousedensitiesV[[3]])
```


### T-test between unique Protein Regions in second ORF and protein coding transcripts:

```{r, echo= FALSE}
cat("Alananine:")
t.test(RIMousedensitiesA[[2]],RIMousedensitiesA[[3]])
cat("Arginine")
t.test(RIMousedensitiesR[[2]],RIMousedensitiesR[[3]])
cat("Asparagine")
t.test(RIMousedensitiesN[[2]],RIMousedensitiesN[[3]])
cat("Aspartic acid")
t.test(RIMousedensitiesD[[2]],RIMousedensitiesD[[3]])
cat("Cysteine")
t.test(RIMousedensitiesC[[2]],RIMousedensitiesC[[3]])
cat("Glutamine")
t.test(RIMousedensitiesQ[[2]],RIMousedensitiesQ[[3]])
cat("Glycine")
t.test(RIMousedensitiesG[[2]],RIMousedensitiesG[[3]])
cat("Glutamic acid")
t.test(RIMousedensitiesE[[2]],RIMousedensitiesE[[3]])
cat("Histidine")
t.test(RIMousedensitiesH[[2]],RIMousedensitiesH[[3]])
cat("Isoleucine")
t.test(RIMousedensitiesI[[2]],RIMousedensitiesI[[3]])
cat("Leucine")
t.test(RIMousedensitiesL[[2]],RIMousedensitiesL[[3]])
cat("Lysine")
t.test(RIMousedensitiesK[[2]],RIMousedensitiesK[[3]])
cat("Methionine")
t.test(RIMousedensitiesM[[2]],RIMousedensitiesM[[3]])
cat("Phenylalanine")
t.test(RIMousedensitiesF[[2]],RIMousedensitiesF[[3]])
cat("Proline")
t.test(RIMousedensitiesP[[2]],RIMousedensitiesP[[3]])
cat("Serine")
t.test(RIMousedensitiesS[[2]],RIMousedensitiesS[[3]])
cat("Threonine")
t.test(RIMousedensitiesT[[2]],RIMousedensitiesT[[3]])
cat("Tryptophan")
t.test(RIMousedensitiesW[[2]],RIMousedensitiesW[[3]])
cat("Tyrosine")
t.test(RIMousedensitiesY[[2]],RIMousedensitiesY[[3]])
cat("Valine")
t.test(RIMousedensitiesV[[2]],RIMousedensitiesV[[3]])
```