---
title: "TranscriptStatistics"
output:
  pdf_document: default
  html_document: default
---

# Human

## Transcript length and Methionine density

```{r Input, echo=FALSE}
splitTranscripts=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-13.21.38_new_NMD/split-ORF_Transcripts_length.tsv',
  sep = '\t', header = FALSE)
splitlengths=splitTranscripts[,2]

nonSplitTranscripts=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-13.21.38_new_NMD/non-split-ORF_Transcripts_length.tsv',
  sep = '\t', header = FALSE)
nonsplitlengths=nonSplitTranscripts[,2]

lengths=c("split-ORF encoding NMD Transcripts"=list(splitlengths), "Remaining NMD Transcripts" = list(nonsplitlengths))


splitTranscriptsDense=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-13.21.38_new_NMD/split-ORF_Transcripts_met_density.tsv',
  sep = '\t', header = FALSE)
splitdensities=splitTranscriptsDense[,2]

nonSplitTranscriptsDense=read.table(
  file = 'G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Output/run_11.02.2021-13.21.38_new_NMD/non-split-ORF_Transcripts_met_density.tsv',
  sep = '\t', header = FALSE)
nonsplitdensities=nonSplitTranscriptsDense[,2]

densities=c("split-ORF encoding NMD Transcripts"=list(splitdensities), "Remaining NMD Transcripts" = list(nonsplitdensities))
```


```{r OutputLength, echo=FALSE}
## Length Distribution and two sided t-test
#boxplot(lengths,ylab="Transcript cDNA length",outline = FALSE)

#t.test(lengths[[1]],lengths[[2]])
```


```{r OutputDensity, echo=FALSE}
## Methionine density Distribution and two sided t-test
#boxplot(densities,ylab="Methionine density of transcript peptide sequence")

#t.test(densities[[1]],densities[[2]])
```

```{r InputCoding, echo=FALSE}
codingTranscripts=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Input/human/Protein_coding_peptide_length.tsv",
  sep = '\t', header = FALSE)
codinglengths=codingTranscripts[,2]

comparelengths=c("split-ORF encoding NMD Transcripts"=list(splitlengths),"Remaining NMD Transcripts" = list(nonsplitlengths), "coding Transcripts" = list(codinglengths))


codingTranscriptsDense=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/Input/human/Protein_coding_peptide_met_density.tsv",
  sep = '\t', header = FALSE)
codingdensities=codingTranscriptsDense[,2]


densitiesCompare=c("split-ORF NMD Transcripts"=list(splitdensities),"Remaining NMD Transcripts" = list(nonsplitdensities), "Coding Transcripts" = list(codingdensities))
```

## Length Distribution and two sided t-test between split-ORF encoding NMD transcripts and coding transcripts


```{r OutputLengthCoding, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(comparelengths,ylab="Transcript cDNA length (bp)",outline = FALSE,main="Length Distribution of NMD transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining NMD transcripts:")
t.test(comparelengths[[1]],comparelengths[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(comparelengths[[1]],comparelengths[[3]])
cat("T-test between remaining NMD transcripts and coding transcripts:")
t.test(comparelengths[[2]],comparelengths[[3]])
```

## Methionine density Distribution and two sided t-test between split-ORF encoding NMD transcripts and coding transcripts


```{r OutputDensityCoding, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(densitiesCompare,ylab="Methionine density of transcript peptide sequence",outline = FALSE,main="Methionine density Distribution of NMD transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining NMD transcripts:")
t.test(densitiesCompare[[1]],densitiesCompare[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(densitiesCompare[[1]],densitiesCompare[[3]])
cat("T-test between remaining NMD transcripts and coding transcripts:")
t.test(densitiesCompare[[2]],densitiesCompare[[3]])
```



```{r InputRI, echo=FALSE}
RIsplitTranscripts=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_split-ORF_Transcripts_DNA_length.tsv",
  sep = '\t', header = FALSE)
RIsplitlengths=RIsplitTranscripts[,2]


RIsplitTranscriptsDense=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_split-ORF_Transcripts_met_density.tsv",
  sep = '\t', header = FALSE)
RIsplitdensities=RIsplitTranscriptsDense[,2]

RINonsplitTranscripts=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_non-split-ORF_Transcripts_DNA_length.tsv",
  sep = '\t', header = FALSE)
RINonsplitlengths=RINonsplitTranscripts[,2]


RINonsplitTranscriptsDense=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_non-split-ORF_Transcripts_met_density.tsv",
  sep = '\t', header = FALSE)
RINonsplitdensities=RINonsplitTranscriptsDense[,2]

RIcomparelengths=c("split-ORF encoding RI Transcripts"=list(RIsplitlengths),"Remaining RI Transcripts" = list(RINonsplitlengths), "coding Transcripts" = list(codinglengths))
RIdensitiesCompare=c("split-ORF encoding RI Transcripts"=list(RIsplitdensities),"Remaining RI Transcripts" = list(RINonsplitdensities), "Coding Transcripts" = list(codingdensities))

```



## Length Distribution and two sided t-test between split-ORF encoding RI transcripts and coding transcripts


```{r OutputLengthCodingRI, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(RIcomparelengths,ylab="Transcript cDNA length (bp)",outline = FALSE,main="Length Distribution of RI transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining RI transcripts:")
t.test(RIcomparelengths[[1]],RIcomparelengths[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(RIcomparelengths[[1]],RIcomparelengths[[3]])
cat("T-test between the remaining RI transcripts and coding transcripts:")
t.test(RIcomparelengths[[2]],RIcomparelengths[[3]])
```

## Methionine density Distribution and two sided t-test between split-ORF encoding RI transcripts and coding transcripts


```{r OutputDensityCodingRI, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(RIdensitiesCompare,ylab="Methionine density of transcript peptide sequence",outline = FALSE,main="Methionine density Distribution of RI transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining RI transcripts:")
t.test(RIdensitiesCompare[[1]],RIdensitiesCompare[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(RIdensitiesCompare[[1]],RIdensitiesCompare[[3]])
cat("T-test between the remaining RI transcripts and coding transcripts:")
t.test(RIdensitiesCompare[[2]],RIdensitiesCompare[[3]])
```



# Mouse

## Transcript length and Methionine density

```{r InputMouse, echo=FALSE}
splitTranscriptsMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/NMD_split-ORF_Transcripts_DNA_mouse_length.tsv",
  sep = '\t', header = FALSE)
splitlengthsMouse=splitTranscriptsMouse[,2]


splitTranscriptsDenseMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/NMD_split-ORF_Transcripts_mouse_met_density.tsv",
  sep = '\t', header = FALSE)
splitdensitiesMouse=splitTranscriptsDenseMouse[,2]

NonsplitTranscriptsMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/NMD_non-split-ORF_Transcripts_DNA_mouse_length.tsv",
  sep = '\t', header = FALSE)
NonsplitlengthsMouse=NonsplitTranscriptsMouse[,2]


NonsplitTranscriptsDenseMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/NMD_non-split-ORF_Transcripts_mouse_met_density.tsv",
  sep = '\t', header = FALSE)
NonsplitdensitiesMouse=NonsplitTranscriptsDenseMouse[,2]

```


```{r InputCodingMouse, echo=FALSE}
codingTranscriptsMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/Protein_coding_DNA_mouse_length.tsv",
  sep = '\t', header = FALSE)
codinglengthsMouse=codingTranscriptsMouse[,2]

comparelengthsMouse=c("split-ORF encoding NMD Transcripts"=list(splitlengthsMouse),"Remaining NMD Transcripts" = list(NonsplitlengthsMouse), "coding Transcripts" = list(codinglengthsMouse))


codingTranscriptsDenseMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/Protein_coding_peptide_mouse_met_density.tsv",
  sep = '\t', header = FALSE)
codingdensitiesMouse=codingTranscriptsDenseMouse[,2]


densitiesCompareMouse=c("split-ORF encoding NMD Transcripts"=list(splitdensitiesMouse),"Remaining NMD Transcripts" = list(NonsplitdensitiesMouse), "Coding Transcripts" = list(codingdensitiesMouse))
```

## Length Distribution and two sided t-test between split-ORF encoding NMD transcripts and coding transcripts


```{r OutputLengthCodingMouse, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(comparelengthsMouse,ylab="Transcript cDNA length (bp)",outline = FALSE,main="Length Distribution of NMD transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining RI transcripts:")
t.test(comparelengthsMouse[[1]],comparelengthsMouse[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(comparelengthsMouse[[1]],comparelengthsMouse[[3]])
cat("T-test remaining RI transcripts and coding transcripts:")
t.test(comparelengthsMouse[[2]],comparelengthsMouse[[3]])
```

## Methionine density Distribution and two sided t-test between split-ORF encoding NMD transcripts and coding transcripts


```{r OutputDensityCodingMouse, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(densitiesCompareMouse,ylab="Methionine density of transcript peptide sequence",outline = FALSE,main="Methionine density distribution of NMD transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining RI transcripts:")
t.test(densitiesCompareMouse[[1]],densitiesCompareMouse[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(densitiesCompareMouse[[1]],densitiesCompareMouse[[3]])
cat("T-test remaining RI transcripts and coding transcripts:")
t.test(densitiesCompareMouse[[2]],densitiesCompareMouse[[3]])
```



```{r InputRIMouse, echo=FALSE}
RIsplitTranscriptsMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_split-ORF_Transcripts_DNA_mouse_length.tsv",
  sep = '\t', header = FALSE)
RIsplitlengthsMouse=RIsplitTranscriptsMouse[,2]


RIsplitTranscriptsDenseMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_split-ORF_Transcripts_mouse_met_density.tsv",
  sep = '\t', header = FALSE)
RIsplitdensitiesMouse=RIsplitTranscriptsDenseMouse[,2]

RINonsplitTranscriptsMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_non-split-ORF_Transcripts_DNA_mouse_length.tsv",
  sep = '\t', header = FALSE)
RINonsplitlengthsMouse=RINonsplitTranscriptsMouse[,2]


RINonsplitTranscriptsDenseMouse=read.table(
  file = "G:/Justin_Backup_29.04.2020/Justin/Uni-Frankfurt/FP+Masterarbeit/PipeTest/Pipeline/shiny/splitORFdatabase/data/RI_non-split-ORF_Transcripts_mouse_met_density.tsv",
  sep = '\t', header = FALSE)
RINonsplitdensitiesMouse=RINonsplitTranscriptsDenseMouse[,2]


RIcomparelengthsMouse=c("split-ORF encoding RI Transcripts"=list(RIsplitlengthsMouse),"Remaining RI Transcripts" = list(RINonsplitlengthsMouse), "coding Transcripts" = list(codinglengthsMouse))
RIdensitiesCompareMouse=c("split-ORF encoding RI Transcripts"=list(RIsplitdensitiesMouse),"Remaining RI Transcripts" = list(RINonsplitdensitiesMouse), "Coding Transcripts" = list(codingdensitiesMouse))

```



## Length Distribution and two sided t-test between split-ORF encoding RI transcripts and coding transcripts


```{r OutputLengthCodingMouseRI, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(RIcomparelengthsMouse,ylab="Transcript cDNA length (bp)",outline = FALSE,main="Length Distribution of RI transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining RI transcripts:")
t.test(RIcomparelengthsMouse[[1]],RIcomparelengthsMouse[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(RIcomparelengthsMouse[[1]],RIcomparelengthsMouse[[3]])
cat("T-test remaining RI transcripts and coding transcripts:")
t.test(RIcomparelengthsMouse[[2]],RIcomparelengthsMouse[[3]])
```

## Methionine density Distribution and two sided t-test between split-ORF encoding RI transcripts and coding transcripts


```{r OutputDensityCodingMouseRI, echo=FALSE, fig.height = 7, fig.width = 10}
boxplot(RIdensitiesCompareMouse,ylab="Methionine density of transcript peptide sequence",outline = FALSE,main="Methionine density distribution of RI transcripts and coding transcripts")

cat("T-test between split-ORF encoding and remaining RI transcripts:")
t.test(RIdensitiesCompareMouse[[1]],RIdensitiesCompareMouse[[2]])
cat("T-test between split-ORF encoding and coding transcripts:")
t.test(RIdensitiesCompareMouse[[1]],RIdensitiesCompareMouse[[3]])
cat("T-test remaining RI transcripts and coding transcripts:")
t.test(RIdensitiesCompareMouse[[2]],RIdensitiesCompareMouse[[3]])
```